Exploratory analysis using Copykat

### 2024-10-15 analyses/cell-type-wilms-tumor-14/exploratory_analysis/03_copykat_SCPCL000850.Rmd
add copycat scripts

---
title: "cell-type-nonETP-ALL-03 Analysis"
author:
  - Your name here
date: "`r Sys.Date()`"
output: html_notebook
---

@@

Load required packages in the following chunk, if needed.
Do not install packages here; only load them with the `library()` function.

```{r packages}
# load required packages
# e.g. library(tidyverse)
```

You may also want to use the `package::function()` syntax within your code for better tracking of which functions come from which packages, and to avoid conflicts between functions with the same name in different packages.

@@

In the chunk below, we include some common directories that you might need, finding their locations using the very useful [`rprojroot` package](https://rprojroot.r-lib.org/).

```{r base paths}
# The base path for the OpenScPCA repository, found by its (hidden) .git directory
repository_base <- rprojroot::find_root(rprojroot::is_git_root)

# The current data directory, found within the repository base directory
data_dir <- file.path(repository_base, "data", "current")

# The path to this module
module_base <- file.path(repository_base, "analyses", "cell-type-nonETP-ALL-03")
```

@@

Set paths to input and output directories and files in the chunk below.

```{r paths}
# Input files

>>>>

---
title: "Exploratory analysis using Copykat"
author: "Jingxuan Chen"
date: "`r Sys.Date()`"
output: html_document
---

@@

```{r packages}
library(dplyr)
library(Seurat)
library(copykat)
library(ggplot2)
```

@@

```{r base paths}
# The base path for the OpenScPCA repository, found by its (hidden) .git directory
path_repo <- rprojroot::find_root(rprojroot::is_git_root)

# The path to this module
path_anal <- file.path(path_repo,"analyses","cell-type-wilms-tumor-14") 
```

@@

Only run for one sample

```{r paths}
library <- "SCPCL000850"
# Input files
